\documentclass{article}
\begin{document}

% \textbf{} setzt den Text in geschweiften Klammern fett ("bf" = Abkürzung für
% "bold face").
\textbf{HAMLET:}
    % Da einige Zeichen in LaTeX eine spezielle Bedeutung haben, dürfen sie
    % nicht einfach im Text verwendet werden. Das beste Beispiel ist das "%".
    % Wenn das Zeichen im Text verwendet wird, macht es den Rest der Zeile zu
    % einem Kommentar. Schau einmal ins PDF, was mit der folgenden
    % Zeile passiert.
    I would like to get a 10% raise.\\

    % Wenn das "%" im Text erscheinen soll, muss es seine besondere Bedeutung
    % verlieren, indem wir ihm einen "\" (Backslash) voranstellen. Das nennt man
    % auch "Escapen" des Zeichens.
    I would like to get a 10\% raise.\\

    % Das müssen wir auch mit den verschiedenen anderen Sonderzeichen
    % machen. Hier eine Auswahl der wichtigsten: \, {}, %, &, $, #, _, ^, ~.
    % Im Text sieht das dann z.B. so aus:
    I earn 10\% percent more than you,
    which results in \$100 USD per \{month\} \& \~ \$ 1000 USD per year.

    % Anführungszeichen sind ebenfalls spezielle Zeichen in LaTeX. Typografisch
    % korrekte Anführungszeichen werden mit "``" und "''" gesetzt.
    ``To be, or not to be'': that is the question:

    % Trenn- und Gedankenstriche sind grundsätzlich zwei verschieden lange
    % Striche. In LaTeX müssen wir sie explizit als solche definieren.
    Opening times: 9-11 AM.\\% Trennstrich
    Hamlet -- written by Shakespeare -- is a nice play.\\% Gedankenstrich
    Hamlet---written by Shakespeare---is a nice play.\\% "englischer" (langer) Gedankenstrich

    To be, or not to be: that is the question:
    Whether 'tis nobler in the mind to suffer
    The slings and arrows of outrageous fortune,
    Or to take arms against a sea of troubles,
    And by opposing end them? To die: to sleep;
    No more; and by a sleep to say we end
    The heart-ache and the thousand natural shocks
    That flesh is heir to, 'tis a consummation
    Devoutly to be wish'd. To die, to sleep;
    To sleep: perchance to dream: ay, there's the rub;
    For in that sleep of death what dreams may come
    When we have shuffled off this mortal coil,
    Must give us pause: there's the respect
    That makes calamity of so long life;

    For who would bear the whips and scorns of time,
    The oppressor's wrong, the proud man's contumely,
    The pangs of despised love, the law's delay,
    The insolence of office and the spurns
    That patient merit of the unworthy takes,
    When he himself might his quietus make
    With a bare bodkin? who would fardels bear,
    To grunt and sweat under a weary life,
    But that the dread of something after death,
    The undiscover'd country from whose bourn
    No traveller returns, puzzles the will
    And makes us rather bear those ills we have
    Than fly to others that we know not of?
    Thus conscience does make cowards of us all;
    And thus the native hue of resolution
    Is sicklied o'er with the pale cast of thought,
    And enterprises of great pith and moment
    With this regard their currents turn awry,
    And lose the name of action.--Soft you now!
    The fair Ophelia! Nymph, in thy orisons
    Be all my sins remember'd.

\textbf{OPHELIA:}
    Good my lord,
    How does your honour for this many a day?

\textbf{HAMLET:}
    I humbly thank you; well, well, well.

\textbf{OPHELIA:}
    My lord, I have remembrances of yours,
    That I have longed long to re-deliver;
    I pray you, now receive them.

\textbf{HAMLET:}
    No, not I;
    I never gave you aught.

\textbf{OPHELIA:}
    My honour'd lord, you know right well you did;
    And, with them, words of so sweet breath composed
    As made the things more rich: their perfume lost,
    Take these again; for to the noble mind
    Rich gifts wax poor when givers prove unkind.
    There, my lord.

\textbf{HAMLET:}
    Ha, ha! are you honest?

\textbf{OPHELIA:}
    My lord?

\textbf{HAMLET:}
    Are you fair?

\textbf{OPHELIA:}
    What means your lordship?

\textbf{HAMLET:}
    That if you be honest and fair, your honesty should
    admit no discourse to your beauty.

\textbf{OPHELIA:}
    Could beauty, my lord, have better commerce than
    with honesty?

\textbf{HAMLET:}
    Ay, truly; for the power of beauty will sooner
    transform honesty from what it is to a bawd than the
    force of honesty can translate beauty into his
    likeness: this was sometime a paradox, but now the
    time gives it proof. I did love you once.

\textbf{OPHELIA:}
    Indeed, my lord, you made me believe so.

\textbf{HAMLET:}
    You should not have believed me; for virtue cannot
    so inoculate our old stock but we shall relish of
    it: I loved you not.

\textbf{OPHELIA:}
    I was the more deceived.

\textbf{HAMLET:}
    Get thee to a nunnery: why wouldst thou be a
    breeder of sinners? I am myself indifferent honest;
    but yet I could accuse me of such things that it
    were better my mother had not borne me: I am very
    proud, revengeful, ambitious, with more offences at
    my beck than I have thoughts to put them in,
    imagination to give them shape, or time to act them
    in. What should such fellows as I do crawling
    between earth and heaven? We are arrant knaves,
    all; believe none of us. Go thy ways to a nunnery.
    Where's your father?

\textbf{OPHELIA:}
    At home, my lord.

\textbf{HAMLET:}
    Let the doors be shut upon him, that he may play the
    fool no where but in's own house. Farewell.

\textbf{OPHELIA:}
    O, help him, you sweet heavens!

\textbf{HAMLET:}
    If thou dost marry, I'll give thee this plague for
    thy dowry: be thou as chaste as ice, as pure as
    snow, thou shalt not escape calumny. Get thee to a
    nunnery, go: farewell. Or, if thou wilt needs
    marry, marry a fool; for wise men know well enough
    what monsters you make of them. To a nunnery, go,
    and quickly too. Farewell.

\textbf{OPHELIA:}
    O heavenly powers, restore him!

\textbf{HAMLET:}
    I have heard of your paintings too, well enough; God
    has given you one face, and you make yourselves
    another: you jig, you amble, and you lisp, and
    nick-name God's creatures, and make your wantonness
    your ignorance. Go to, I'll no more on't; it hath
    made me mad. I say, we will have no more marriages:
    those that are married already, all but one, shall
    live; the rest shall keep as they are. To a
    nunnery, go.

\textbf{OPHELIA:}
    O, what a noble mind is here o'erthrown!
    The courtier's, soldier's, scholar's, eye, tongue, sword;
    The expectancy and rose of the fair state,
    The glass of fashion and the mould of form,
    The observed of all observers, quite, quite down!
    And I, of ladies most deject and wretched,
    That suck'd the honey of his music vows,
    Now see that noble and most sovereign reason,
    Like sweet bells jangled, out of tune and harsh;
    That unmatch'd form and feature of blown youth
    Blasted with ecstasy: O, woe is me,
    To have seen what I have seen, see what I see!

\end{document}
